\documentclass[qipps.tex]{subfiles}

\begin{document}
\section{Approach}

\subsection{Target Groups}
\ifdraft{
\begin{itemize}
\item Briefly describe the target group(s) this project will be aimed at. include a rationale for why they were selected.
\item If relevant, select one or more geographical locations and/or settings for this project. 
\begin{itemize}
\item Geographic location
\item Setting
\end{itemize}
\item Define one or more target group demographics for this project. Enter information into the table below.
\begin{itemize}
\item Life course
\item Gender
\item Ethnic background
\item SES status
\end{itemize}
\item What opportunities or capacities already exist within the target group(s)?
\item How will the target group and community stakeholders be encouraged to actively participate and engage with the project?
\end{itemize}

}{}

%--------------------------------------------------
% Write response below this
%--------------------------------------------------
% \taburowcolors 5{green!25 .. yellow!50}
\begin{tabu} to 170mm {|X[c]|X[c]|X[c]|X[c]|} \hline
Lifecourse & Gender & Ethnic Background & SES Status \\ \hline
    &   &    &      \\ \hline
\end{tabu}


%---------------------------------------------------------
\subsection{Ethics and Equity}
\ifdraft{
\begin{itemize}
\item Does this project require ethics approval?
\item Describe the steps that have been taken to ensure that this project is equitable and ethical.
\item Does this project require health impact assessment?
\end{itemize}
}{}
%---------------------------------------------------------
% Write response below this
%---------------------------------------------------------


%---------------------------------------------------------
\subsection{Models and Frameworks}
\ifdraft{
Identify the models and/or frameworks that apply to this project. Include a rationale for why they were selected. 
Explain the Model/Framework
}{}
%------------------------------------------------
% write your stuff under here
%-----------------------------------------------

\end{document}