\documentclass[qipps.tex]{subfiles}

\begin{document}
\section{Working On This Document}
\subsection{Required Software}
You will need to have installed the following Free and OpenSource Software:
\begin{itemize}
\item the template for this document is available from \url{https://github.com/morpheusbeing/qipps}
\item \LaTeXe\ typography and typesetting language using TeXlive\cite{TXUG2016}, packages are available for MS Windows, Gnu Linux and Apple MACOSX.
\item editing with TeXstudio\cite{TXDT2016}.
\item bibliography management with JabRef\cite{JRPT2016} which also needs latest version of Java Runtime to be installed.
\item if you require images, you will need GIMP\cite{GIMPDT2016} and Inkscape\cite{IDT2016}.
\item for statistics and charts you will need RStudio\cite{RSDT2016} and R\cite{RPT2016}.
\end{itemize}

Please ensure that you download and install in the order given in the above list.

\subsection{Editing}
\begin{itemize}
\item Make sure you add your references to quipps.bib using JabRef as you go.
\item Using TeXstudio, set quipps.tex as the root document using Options->Root Document->Set Current Document
\item Edit the header and footer sections as required to reflect the project name, organisation name etc.
\item Edit each file as required adding your content answering the questions, following the guidelines.
\item Compile and create pdf document by clicking on the double green arrow. Sometimes you may have to use Tools->Bibliography to solve problems with getting the references correct.
\item To get the page number of maximum page number, please build at least twice to set all the required variables.
\item When you are happy with the Draft and ready for final output, edit the top lines in quipps.tex where indicated to change from draft to final version.
\item Repeat as necessary.
\end{itemize}
\end{document}
